\section{Limitations}

The MATLAB behavioural model is simplified. It uses a finite-gain, finite-bandwidth abstraction and does not claim to capture detailed vendor pole-zero behaviour, output swing limits, nonlinearities, package parasitics, layout parasitics, or device-level noise behaviour.

The Safe/Marginal/Risky regions are project-defined screening categories. They are not universal engineering standards or certified stability labels. They organize the current sweep outputs and help select cases for later review.

The vendor macromodel comparison is simulation-only. OP27, OPA818, and ADA4817 macromodel cases are real vendor-model export comparisons, but they are not hardware measurements. They do not constitute complete SPICE coverage, process/temperature coverage, layout extraction, or experimental validation.

The noise analysis is first-pass behavioural estimation only. The current project does not include measured detector noise, measured output noise, or SPICE noise analysis. The noise figures support relative discussion under stated assumptions, not final device claims.

The literature review remains in progress. Several useful DOI-only sources are available only at abstract or metadata level and are not used for detailed claims. Detailed receiver front-end and low-noise receiver comparisons remain future work until full text is available and read. Table~\ref{tab:source-confidence} documents the current source-usage confidence boundary as one grouped confidence table; it may move to an appendix after target journal selection.

The package remains a manuscript-development prototype. It is not a final Q3 submission-ready manuscript. Final readiness requires close reading notes, final captions, a verified final bibliography, target-format editing, and supervisor or domain review.

\section{Conclusion}

This generic LaTeX draft presents a MATLAB-and-SPICE-assisted workflow for photodiode TIA design-region mapping under finite op-amp bandwidth constraints. The workflow combines a simplified MATLAB behavioural model, feedback-capacitance sweeps, project-defined design-region maps, vendor macromodel comparison for OP27, OPA818, and ADA4817, and first-pass behavioural noise estimates. The evidence is traceable through committed scripts, CSV files, figures, and prepaper planning documents.

The defensible contribution is a reproducible early-stage screening workflow for photodiode TIA design exploration. The work organizes how feedback capacitance, photodiode capacitance, finite op-amp bandwidth, peaking, and first-pass noise assumptions interact under selected conditions. The literature context shows that bandwidth enhancement, regulated-cascode structures, inductorless CMOS TIAs, and noise-aware optical receiver front ends are established topics, so the project is positioned as a workflow contribution rather than a new circuit topology.

Future work includes deeper full-text reading, full reference formatting, target-journal figure and caption polish, additional vendor macromodel cases if needed, optional SPICE noise analysis, and independent review of modelling assumptions. Hardware measurement and measured-noise validation remain outside the current evidence package.
