\section{Limitations}

The MATLAB behavioural model is simplified. It uses a finite-gain, finite-bandwidth abstraction and explicit scalar total input-node capacitance. It does not claim to capture detailed vendor pole-zero behaviour, output swing limits, nonlinearities, package parasitics, layout parasitics, or device-level noise behaviour.

The agreement analysis uses documented vendor-specific $C_{in}$ values where available, but $C_{\mathrm{stray}}$ is set to zero and is not fitted. Vendor-specific open-loop gain and detailed open-loop dynamics remain approximate or manual-check assumptions. The no-$C_{in}$ versus documented-$C_{in}$ ablation shows mixed and modest changes for the current $C_{pd}=10$ pF vendor rows, so the draft does not claim that $C_{in}$ uniformly improves agreement.

The Safe/Marginal/Risky regions are project-defined screening categories. They are not universal engineering standards or certified stability labels. They organize the current sweep outputs and help select cases for later review.

The behavioural-vs-vendor agreement analysis is simulation-only. OP27, OPA818, and ADA4817 macromodel cases are vendor-model export comparisons, but they are not hardware measurements. OP27 is included as a low-GBW negative-control or illustrative limitation case, not as primary high-speed TIA evidence. The vendor macromodel summaries do not constitute complete SPICE coverage, process/temperature coverage, layout extraction, or experimental validation.

The noise analysis is first-pass behavioural estimation only. The current noise scripts use a 1 nA photodiode current assumption for the enabled shot-noise term, but the noise helper has not yet been updated to carry $C_{\mathrm{total}}$ through the voltage-noise transfer expression. The current study does not include measured detector noise, measured output noise, or SPICE noise analysis. The noise figures support relative discussion under stated assumptions, not final device claims.

The literature review remains intentionally short. Several useful DOI-only sources are available only at abstract or metadata level and are not used for detailed claims. Detailed receiver front-end and low-noise receiver comparisons remain future work until full text is available and read. Source-scope documentation is kept in repository notes and README material rather than compiled as a main manuscript table in this draft.

\section{Reproducibility: Code and Data Availability}

The report is intended to be reproducible from the accompanying repository. The MATLAB behavioural scripts are stored under \texttt{tia\_extension/scripts/}, generated CSV summaries under \texttt{tia\_extension/results/}, and generated figures under \texttt{tia\_extension/figures/}. The repository README and TIA-extension README include a figure/table-to-script crosswalk that maps each manuscript artifact to the script, CSV source, and figure asset used in the draft.

The current reproducibility package uses existing repository data only. The main behavioural scripts regenerate the baseline response, feedback-capacitance sweep, design-region map, representative responses, first-pass noise figures, behavioural-vs-vendor agreement summary, and input-capacitance ablation summary. The Overleaf draft bundles copied figure assets for portability, but those copied assets are not the source of record.

Vendor macromodel use requires caution. Public release should document where vendor macromodels were obtained and provide wrapper/testbench material plus extracted summaries where redistribution is permitted; vendor model source files remain subject to vendor licence terms. A permanent repository DOI should be minted through a release archive service such as Zenodo before public citation. Until that release exists, repository and DOI fields remain placeholders.

\section{Conclusion}

This work presents a MATLAB- and vendor-macromodel-assisted workflow for early-stage photodiode TIA design screening under finite op-amp bandwidth and input-node capacitance constraints. The workflow combines a simplified MATLAB behavioural model, feedback-capacitance sweeps, project-defined design-region maps, quantified behavioural-vs-vendor agreement checks for OP27, OPA818, and ADA4817, and first-pass behavioural noise estimates. The evidence is traceable through repository scripts, CSV files, figures, and manuscript-preparation notes.

The defensible contribution is a reproducible early-stage screening workflow for photodiode TIA design exploration. The work organizes how feedback capacitance, photodiode capacitance, finite op-amp bandwidth, peaking, selected vendor macromodel exports, and first-pass noise assumptions interact under selected conditions. The literature context shows that bandwidth enhancement, regulated-cascode structures, inductorless CMOS TIAs, and noise-aware optical receiver front ends are established topics, so the study is positioned as a workflow contribution rather than a new circuit topology.

Future work includes deeper full-text reading, final reference formatting, target-format editing, additional vendor macromodel cases if needed, optional SPICE noise analysis, and independent review of modelling assumptions. Hardware measurement and measured-noise validation remain outside the current evidence package.
